Gaussian mean estimation in simulated data sets

### 2018-12-04 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

Since the simulation experiments are computationally intensive, they
are implemented separately (see the "dsc" directory in this git
repository), and here we only create plots to summarize the results of
these experiments.

@@

This plot reproduces Fig. 2 of the manuscript comparing the
accuracy of estimated mean curves in the data sets simulated from
the "Spikes" mean function with constant variance.

@@

From this plot, we see that three versions of SMASH outperformed
EbayesThresh and TI thresholding.

@@

In this scenario, data sets were simulated using the "Spikes" mean
function and the "Clipped Blocks" variance function. The next couple
plots reproduce part of Fig. 3 in the manuscript.

@@

In the "Spikes" scenario, we see that SMASH, when allowing for
heteroskedastic errors, outperforms EbayesThresh and all variants of
TI thresholding (including TI thresholding with the true variance).
Further, SMASH performs almost as well when estimating the variance
compared to when provided with the true variance.

@@

In this next scenario, the data sets were simulated using the "Corner"
mean function and the "Doppler" variance function. These plots were
also used for Fig. 3 of the manuscript.

>>>>

Since the simulation experiments are computationally intensive, they
were implemented separately (see the "dsc" directory in this git
repository), and here we only create plots to summarize the results of
these experiments.

@@

This plot reproduces Fig. 2 of the manuscript, which compares the
accuracy of the mean curves estimated from the data sets that were
simulated using the "Spikes" mean function with constant variance.

@@

From this plot, we see that the three variations of SMASH all
outperformed EbayesThresh and TI thresholding in this setting.

@@

In this scenario, the data sets were simulated using the "Spikes" mean
function and the "Clipped Blocks" variance function. The next two
plots reproduce part of Fig. 3 in the manuscript.

@@

In this scenario, we see that SMASH, when allowing for heteroskedastic
errors, outperforms EbayesThresh and all variants of TI thresholding
(including TI thresholding when provided with the true variance).
Further, SMASH performs almost as well when estimating the variance
compared to when provided with the true variance.

@@

In this next scenario, the data sets were simulated using the "Corner"
mean function and the "Doppler" variance function. These plots were
also used in Fig. 3 of the manuscript.
